Towards a classification framework for social machines

### 2013-02-26 latex/paper_new.tex
Added missing hline in table

\begin{table}[htb]
\begin{center}
\begin{scriptsize}
\begin{tabular}{|p{8cm}|}
\hline
{\bf Tasks, purpose and context of participation} \\
\hline
Activities involve creative production of content \\
Activities involve subjective appraisal of content \\
Activities involve solving (a definable) computation task or set of problems\\
Tasks are domain-specific \\
The machine owner derives benefit from participation \\
Activities and tasks are pre-defined or participant-defined \\
Variation in types of contributions and tasks \\
Participants' participate to fulfil needs of a role \\
\hspace{1cm} work-related/professional role \\
\hspace{1cm} home/family related \\
\hspace{1cm} social role \\
\hspace{1cm} leisure/entertainment role \\
Participation is done via: \\
\hspace{1cm} mobile devices \\
\hspace{1cm} Web browsers \\
\hspace{1cm} apps \\
\hspace{1cm} sensors/sensing (location sensing and wearable devices) \\
Participation is done in a mobile context \\
\hspace{1cm} Physical location is relevant to the service \\
\hline
{\bf Participants and roles} \\
\hline
Generality of audience \\
Participant autonomy \\
Participant anonymity \\
Extent of hierarchical organisation of roles \\
Clear separation of roles among participants \\
{\bf Motivation and incentives} \\
\hline
Participants are intrinsically motivated:\\
\hspace{1cm} to gain/share knowledge \\
\hspace{1cm} to ``get something done'' \\
\hspace{1cm} to ``for fun/entertainment''\\
\hspace{1cm} to ``be social'' \\
\hspace{1cm} for the benefit of a specific group of people who need help \\
\hspace{1cm} for the benefit of society as a whole \\
Participation is motivated by extrinsic reward (payment, status) \\
\hline

>>>>

\begin{table}[htb]
\begin{center}
\begin{scriptsize}
\begin{tabular}{|p{8cm}|}
\hline
{\bf Tasks, purpose and context of participation} \\
\hline
Activities involve creative production of content \\
Activities involve subjective appraisal of content \\
Activities involve solving (a definable) computation task or set of problems\\
Tasks are domain-specific \\
The machine owner derives benefit from participation \\
Activities and tasks are pre-defined or participant-defined \\
Variation in types of contributions and tasks \\
Participants' participate to fulfil needs of a role \\
\hspace{1cm} work-related/professional role \\
\hspace{1cm} home/family related \\
\hspace{1cm} social role \\
\hspace{1cm} leisure/entertainment role \\
Participation is done via: \\
\hspace{1cm} mobile devices \\
\hspace{1cm} Web browsers \\
\hspace{1cm} apps \\
\hspace{1cm} sensors/sensing (location sensing and wearable devices) \\
Participation is done in a mobile context \\
\hspace{1cm} Physical location is relevant to the service \\
\hline
{\bf Participants and roles} \\
\hline
Generality of audience \\
Participant autonomy \\
Participant anonymity \\
Extent of hierarchical organisation of roles \\
Clear separation of roles among participants \\
\hline
{\bf Motivation and incentives} \\
\hline
Participants are intrinsically motivated:\\
\hspace{1cm} to gain/share knowledge \\
\hspace{1cm} to ``get something done'' \\
\hspace{1cm} to ``for fun/entertainment''\\
\hspace{1cm} to ``be social'' \\
\hspace{1cm} for the benefit of a specific group of people who need help \\
\hspace{1cm} for the benefit of society as a whole \\
Participation is motivated by extrinsic reward (payment, status) \\
\hline
